Data analysis to support temporary cycleways

### 2020-04-30 README.Rmd
Update description of maps

The results below show all roads with a 'spare lane' in the low average traffic conditions created by the partial lockdown (light blue) plus the top 10 roads of a minimum length in terms of estimated cycling potential under the Government Target scenario in the PCT.

>>>>

The results below show all roads with a 'spare lane' in the low average traffic conditions created by the partial lockdown (light blue) based on the three criteria listed above (lanes, potential and length) plus the top 10 roads of a minimum length in terms of estimated cycling potential under the Government Target scenario in the PCT (dark blue).
